Neural Neural Textures Make Sim2Real Consistent

### 2022-06-24 CORL/example.tex
Added figure0
Added robot arm animation
Updates from Overleaf

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}

>>>>

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=\textwidth]{../images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\psi, \ell_{UC}, \ell_{TR}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}
